A Causal Model of \hbox{DBMS} Suboptimality\\

### 2017-08-08 subopt-tods17/paper.tex
TODS submission on the subopt

Through a series of experiments that examine the plans for thousands of
queries run on one hundred thousand query/cardinality combinations on four
popular DBMSes, we observe that the dependent construct of empirical
suboptimality prevalence correlates positively with (a)~\hbox{DBMS}
complexity, (b)~schema complex, (c)~data complexity, and (d)~query
complexity, providing empirical support for this model. These
\discont{ten}{nine} factors explain in concert over half of the
variance of suboptimality, across four disparate DBMSes. Thus, it is the
common aspects of these DBMSes that predict
suboptimality, {\em not} the particulars embedded in the inordinate complexity of
each of these DBMSes.

>>>>

Through a series of experiments that examine the plans for thousands of
queries run on one hundred thousand query/cardinality combinations on four
popular DBMSes, we observe that the dependent construct of empirical
suboptimality prevalence correlates positively with (a)~\hbox{DBMS}
complexity, (b)~schema complexity, (c)~data complexity, and (d)~query
complexity, providing empirical support for this model. These
\discont{ten}{nine} factors explain in concert over half of the
variance of suboptimality, across four disparate DBMSes. Thus, it is the
common aspects of these DBMSes that predict
suboptimality, {\em not} the particulars embedded in the inordinate complexity of
each of these DBMSes.
